\documentclass[12pt]{article}

\usepackage{geometry}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 right=10mm,
 top=10mm,
 bottom=20mm,
 headheight=75pt
 }
% \usepackage[utf8x]{inputenc}
\usepackage{fontspec}
\setmainfont{Open Sans}
\setsansfont{Noto Sans}
\usepackage{graphicx}
\usepackage{forloop}
\usepackage{subcaption}
\usepackage{url}       % `\url`s
\usepackage{floatrow}
\usepackage{hyperref}
\usepackage{cleveref}
\graphicspath{{resources_quiz_1/}}

\usepackage{fancyhdr}
\pagestyle{fancy}


\renewcommand{\headrulewidth}{0pt}
% \fancyhead[C]{}
% \fancyfoot[]{}


\newcommand\pic[1]{(\cref{#1})} %Где нужно сослаться на рисунок

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=cyan,
    }

% The preamble ends with the command \begin{document}
\begin{document}
\begin{center}
    \LARGE <<Mechanics and Machines>> \\ \textbf{Test 2}
\end{center}

\textbf{Task 1}
\begin{enumerate}
    \item You are a cleaning robot developer. You know proposed characteristics of robot inertia, and you should choose the motors for it. Robot kinematics is 2 wheel robot, with 2 supports.

    Explain your steps for choosing the motor.
\end{enumerate}

\textbf{Task 2}
\begin{enumerate}
    \item What the difference between rolling friction and sliding friction? 
\end{enumerate}

\textbf{Task 3}
\begin{enumerate}
    \item What types of synthesis do we have? What the main difference between them?
    \item Propose the problem of structural synthesis and the steps what should you do for solving it?
    \item What the difference between function generation and trajectory generation synthesis problems?
\end{enumerate}

\textbf{Task 4}
\begin{enumerate}
    \item Bearings. Types. Prof and cons. How to mount and dismount them. The idea besides locating and floating bearings.
    \item Screw types. Type of drills. Type of holes. How to distinguish them on a blueprints?
\end{enumerate}

\textbf{Task 5}
\begin{enumerate}
    \item What types of permanent connections do you know (at least 4)? Examples. Benefits and withdraws
    \item What types of detachable connections do you know (at least 4)? Examples. Benefits and withdraws
\end{enumerate}

\textbf{Task 6}
\begin{enumerate}
    \item Types of manufacturing. At least 1 example for each type. Prof and cons.
\end{enumerate}


\end{document}